Films: Age & Gender

### 2017-08-26 01_actor_careers/05_report.Rmd
theme update

@@

# Highcharts theme
source()
tmbish = high_tmbish()
```

@@

films = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_full_film_data.csv") %>% filter(!is.na(title))

@@

# library(gender)
# library(stringr)
# library(lubridate)
# 
# film_folk = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_actors_directors.csv")
# 
# # Clean some data quality issues on the DOB
# film_folk[film_folk$dob < as.Date("1880-01-01"), "dob"] = as.Date("1880-01-01")
# 
# # Grep out first name and dob year for the gender function
# film_folk =
#   film_folk %>%
#   mutate(
#     first_name = str_extract(name, "(?i)[a-z]+(?=\\s)"),
#     dob_year = year(dob)
#   )
# 
# # Distinct name, dob combos and predict gender
# genders =
#   film_folk %>%
#   distinct(first_name, dob_year) %>%
#   gender_df(name_col = "first_name", year_col = "dob_year") %>%
#   select("first_name" = name, gender, "dob_year" = year_min)

@@

We should sense check the gender mapping. Let's take a random 10 people to check is working as desired:

```{r}
set.seed(123)

genders %>%
  sample_n(10) %>%
  knitr::kable(caption = "Sense Checking the Gender Mapping")

Things get dicey with a name like Sandy; however, the package obviously knows that most Sandys born in 1937 were female so we'll have to trust it here. Otherwise the list looks pretty, pretty, pretty good.

@@

# Q1. Gender Gap

To answer this question we'll first need to calculate a person's age at the time of their appearance in a film. We'll then

@@

```{r echo = FALSE}
chart
```

>>>>

# For reproducibility
set.seed(123)

@@

# Highcharts theme
source("https://raw.githubusercontent.com/TMBish/lab_posts/master/highcharts_theme.R")
tmbish = high_tmbish()
```

@@

```{r}
# Load in films data from Github Repo
films = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_full_film_data.csv") %>% filter(!is.na(title))

@@

library(gender)
library(stringr)
library(lubridate)

film_folk = read_csv("https://raw.githubusercontent.com/TMBish/lab_posts/master/01_actor_careers/00_actors_directors.csv")

# Clean some data quality issues on the DOB
film_folk[film_folk$dob < as.Date("1880-01-01"), "dob"] = as.Date("1880-01-01")

# Grep out first name and dob year for the gender function
film_folk =
  film_folk %>%
  mutate(
    first_name = str_extract(name, "(?i)[a-z]+(?=\\s)"),
    dob_year = year(dob)
  )

# Distinct name, dob combos and predict gender
genders =
  film_folk %>%
  distinct(first_name, dob_year) %>%
  gender_df(name_col = "first_name", year_col = "dob_year") %>%
  select("first_name" = name, gender, "dob_year" = year_min)

@@

We should sense check the gender mapping to make sure the package is making logical inferences. Let's take a random 10 person sample:

```{r}
genders %>%
  sample_n(10) %>%
  knitr::kable()
```

So generally this is looking pretty, pretty good. Things get dicey with unisex names like Sandy; however, the package must know that most Sandys born in 1937 were female so we'll have to trust it here. Finally we'll need to join this information back to the individual data set.

@@

# Female Directors?

# How old?

We've finally sorted out our source data. However, we still need to add a few variables to be able to answer this question. We need we'll first need to calculate a person's age at the time of their appearance in a film. We'll then

@@

```{r echo = FALSE}
rating_chart
```
